---
title: "S1_QC"
author: "Kareem"
date: "2023-03-14"
output: html_document
---
#Load Packages
```{r}
library(Seurat)
library(ggplot2)
library(dplyr)
library(clustree)
library(tidyverse)
```
#Load Object
```{r}
setwd("/Users/woodskad/Desktop/Analysis/S1/")
load("/Users/woodskad/Desktop/Analysis/S1/Robject/glut_subset_forthpipe_11102022.RData")
load("/Users/woodskad/Desktop/Analysis/S1/Robject/gaba_subset_forthpipe_03142023.RData")
```

#GLUT SUBSET
#Glut Vlnplot (Genes Expressed)
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/Glut/GlutVln_Gene_ExpV4.pdf",
    width = 2,
    height = 2)
VlnPlot(glut.subset2, 
        features = c("nFeature_RNA"), 
        pt.size = 0, 
        ncol = 1,
        flip = T) + 
  coord_flip() + 
  theme(legend.position = "none") + 
  theme(axis.title = element_blank()) +
  ggtitle(NULL)
dev.off()
```

#Glut Vlnplot (Transcripts Expressed)
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/Glut/GlutVln_transcriptsV4.pdf",
    width = 2,
    height = 2)
VlnPlot(glut.subset2, 
        features = c("nCount_RNA"), 
        pt.size = 0, 
        ncol = 1,
        flip = T) + 
  coord_flip() +
  theme(legend.position = "none") + 
  theme(axis.title = element_blank()) +
  ggtitle(NULL)
dev.off()
```


#UMAP Glut Group by Cartridge
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/GlutUMAP_CartV3.pdf",
    width = 10,
    height = 10)
DimPlot(glut.subset2, 
        group.by = "orig.ident", 
        shuffle = T) + 
  theme_void() + 
  theme(legend.position = "none") + 
  ggtitle(NULL)
dev.off()
```

#UMAP Glut Group by Group
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/GlutUMAP_GroupV2.pdf",
    width = 10,
    height = 10)
DimPlot(glut.subset2, 
        group.by = "group", 
        shuffle = T) + 
  theme_void() + 
  theme(legend.position = "none") + 
  ggtitle(NULL)
dev.off()
```

#UMAP Glut Group by Sex
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/GlutUMAP_SexV2.pdf",
    width = 10,
    height = 10)
DimPlot(glut.subset2,
        group.by = "sex", 
        cols = c("skyblue2", "violetred3"), 
        shuffle = T) + 
  theme_void() + 
  theme(legend.position = "none") + 
  ggtitle(NULL)
dev.off()
```

#UMAP Glut Group by RatID
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/GlutUMAP_RatIDV2.pdf",
    width = 10,
    height = 10)
DimPlot(glut.subset2, 
        group.by = "ratID", 
        shuffle = T) + 
  theme_void() + 
  theme(legend.position = "none") + 
  ggtitle(NULL)
dev.off()
```



#GABA SUBSET
#Gaba Vlnplot (Genes Expressed)
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/Gaba/GabaVln_Gene_ExpV3.pdf",
    width = 2,
    height = 2)
VlnPlot(gaba.subset2, 
        features = c("nFeature_RNA"), 
        pt.size = 0, 
        ncol = 1, 
        flip = T) + 
  coord_flip() + 
  theme(legend.position = "none") + 
  theme(axis.title = element_blank()) +
  ggtitle(NULL)
dev.off()
```

#Gaba Vlnplot (Transcripts Expressed)
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/Gaba/GabaVln_transcriptsV3.pdf",
    width = 2,
    height = 2)
VlnPlot(gaba.subset2, 
        features = c("nCount_RNA"), 
        pt.size = 0, 
        ncol = 1, 
        flip = T) + 
  coord_flip() + 
  theme(legend.position = "none") + 
  theme(axis.title = element_blank()) +
  ggtitle(NULL)
dev.off()
```

#UMAP Gaba Group by Cartridge
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/Gaba/GabaUMAP_CartV3.pdf",
    width = 10,
    height = 10)
DimPlot(gaba.subset2, 
        group.by = "orig.ident", 
        shuffle = T) + 
  theme_void() + 
  theme(legend.position = "none") + 
  ggtitle(NULL)
dev.off()
```

#UMAP Gaba Group by Group
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/Gaba/GlutUMAP_GroupV2.pdf",
    width = 10,
    height = 10)
DimPlot(gaba.subset2, 
        group.by = "group", 
        shuffle = T) + 
  theme_void() + 
  theme(legend.position = "none") + 
  ggtitle(NULL)
dev.off()
```

#UMAP Gaba Group by Sex
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/Gaba/GlutUMAP_SexV2.pdf",
    width = 10,
    height = 10)
DimPlot(gaba.subset2, 
        group.by = "sex", 
        cols = c("skyblue2", "violetred3"), 
        shuffle = T) + 
  theme_void() + 
  theme(legend.position = "none") + 
  ggtitle(NULL)
dev.off()
```

#UMAP Gaba Group by RatID
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/Gaba/GabaUMAP_RatIDV2.pdf",
    width = 10,
    height = 10)
DimPlot(gaba.subset2, 
        group.by = "ratID", 
        shuffle = T) + 
  theme_void() + 
  theme(legend.position = "none") + 
  ggtitle(NULL)
dev.off()
```

#Glut Heatmap 
#Find Glut Markers
```{r}
glut.markers <- FindAllMarkers(glut.subset2, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
glut.markers %>% 
  group_by(cluster) %>% 
  top_n(n = 10, wt = avg_log2FC) -> top10.glut
```
#Create Heatmap
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/Heatmaps/glut_top10genes_heatmapV2.pdf",
    width = 7,
    height = 7)
glut.heatmap <- DoHeatmap(glut.subset2, features = top10.glut$gene, raster = FALSE) 
glut.heatmap

dev.off()
```


#Gaba Heatmap 
#Find Gaba Markers
```{r}
gaba.markers <- FindAllMarkers(gaba.subset2, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25) 
gaba.markers %>% 
  group_by(cluster) %>% 
top_n(n = 10, wt = avg_log2FC) -> top10.gaba
```
#Create Heatmap
```{r}
pdf(file = "/Users/woodskad/Library/CloudStorage/Box-Box/mRFP-snSeq/Project1_XPoSEseq/XPoSEseq_manuscript/S1_panels/Heatmaps/gaba_top10genes_heatmapV2.pdf",
    width = 7,
    height = 7)
gaba.heatmap <- DoHeatmap(gaba.subset2, features = top10.gaba$gene, raster = FALSE) 
gaba.heatmap

dev.off()
```

